Guarded Recursion in Agda via Sized Types

### 2019-02-03 code-oneclock-paper/latex/paper.tex
Fixes in conclusion

\section{Conclusions and Future Work}
\label{sec:concl}
We presented a simple type theory for guarded recursion that we called \GTT. We
formalized its syntax and semantics in Agda. Crucially, sized types
were employed for giving an interpretation to the characteristic
features of guarded recursion. From this we conclude that guarded
recursion can be simulated using sized types. We greatly benefited
of the fact that sized types constitute a native feature of Agda, so
we were able to fully develop our theory inside a proof assistent.

This work can be extended in several different directions.
Various type theories for guarded recursion in the literature include
dependent types. Currently, there exist two disciplines for mixing
dependent types with guarded recursion: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
the syntax and semantics of \GTT\ with dependent types following one
of these methods.

@@

Finally, we want to understand weather it is possible to reduce sized
types to guarded recursion.  This does not seems directly doable,
since sizes are not uniquely employed with coinductive types as a tool
for easing the productivity check of corecursive definitions, but they
are also used as auxiliary arguments of inductive types for
facilitating the termination check of recursive definitions. It seems
that, in order to capture this dual aspect of sizes, one needs to
extend the existing type theories for guarded recursion with
additional features.
%%
%% Bibliography
%%

>>>>

\section{Conclusions and Future Work}
\label{sec:concl}
We presented a simple type theory for guarded recursion that we called \GTT. We
formalized its syntax and semantics in Agda. Sized types
were employed to interpret the characteristic
features of guarded recursion. From this, we conclude that guarded
recursion can be simulated using sized types. We greatly benefited
of the fact that sized types constitute a native feature of Agda, so
we were able to fully develop our theory inside a proof assistent.

This work can be extended in several different directions.
Various type theories for guarded recursion in the literature include
dependent types. Currently, there are two disciplines for these two features: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
the syntax and semantics of \GTT\ with dependent types following one
of these methods.

@@

Finally, we want to understand whether it is possible to reduce sized
types to guarded recursion.  This does not seems directly doable,
since sizes are not uniquely employed with coinductive types as a tool
for easing the productivity check of corecursive definitions, but they
are also used as auxiliary arguments of inductive types for
facilitating the termination check of recursive definitions. It seems
that, in order to capture this dual aspect of sizes, one %needs to
%extend the existing type theories for guarded recursion with
%additional features.
%%
%% Bibliography
%%
